Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph for Community Detection and Parameter Estimation

### 2021-06-30 summary.tex
typo

\begin{definition}[Popularity Adjusted Block Model]
\label{pabm}
Let $P \in [0, 1]^{n \times n}$ be a symmetric edge probability matrix for a
graph $G = (V, E)$ with adjacency matrix $A$ such that $A \sim \BG(P)$.
Let each vertex have a community label between $1$ and $K$.
Then $G$ is drawn from a Popularity Adjusted Block Model if
each vertex has $K$ popularity parameters that describe its affinity
toward each of the $K$ communities, i.e., vertex $i$ has popularity parameters
$\lambda_{i1}, ..., \lambda_{iK}$, and
each $P_ij = \lambda_{i z_j} \lambda_{j z_i}$.

>>>>

\begin{definition}[Popularity Adjusted Block Model]
\label{pabm}
Let $P \in [0, 1]^{n \times n}$ be a symmetric edge probability matrix for a
graph $G = (V, E)$ with adjacency matrix $A$ such that $A \sim \BG(P)$.
Let each vertex have a community label between $1$ and $K$.
Then $G$ is drawn from a Popularity Adjusted Block Model if
each vertex has $K$ popularity parameters that describe its affinity
toward each of the $K$ communities, i.e., vertex $i$ has popularity parameters
$\lambda_{i1}, ..., \lambda_{iK}$, and
each $P_{ij} = \lambda_{i z_j} \lambda_{j z_i}$.
